A holomorphic approach to membranes and fivebranes

### 2022-07-21 fivebranes/index.tex

\subsection{States in twisted supergravity}

In eleven-dimensional supergravity, the ${\rm AdS}_7 \times S^4$ and ${\rm AdS}_{4}\times S^{7}$ backgrounds are obtained by backreacting a number of fivebranes and membranes respectively in flat space \cite{Maldacena:1997re,WittenAdS}.
In \cite{RSW} we gave descriptions of twisted versions of these backgrounds. We will recall this construction, adapted to a slightly more global situation than is considered in \textit{loc. cit.}.

@@

  \item Deform the theory on the complement of the zero section by a certain Maurer--Cartan element.
  The Maurer--Cartan element is thought of as the flux sourced by branes wrapping the zero section.

  \item The complement of the zero section is a manifold with boundary---we impose a natural boundary condition.

\end{itemize}

\parsec[s:brkevin]

As a way to highlight the key aspects of the construction, we consider the simplified model of Costello's twisted $M$ theory on $\R \times \T^* C$, where $C$ is a Riemann surface equipped with a nonvanishing holomorphic one-form $\d z$, with some number of twisted `fivebranes' wrapping the zero section
\[
0 \times C \subset \R \times \T^* C .
\]
Denote by $t$ the real coordinate and by $w$ the fiber coordinate in $\T^* C$.
If we remove the defect we obtain the manifold 
\[
\left(\R \times \T^* C\right) - C \simeq C \times \R_{>0} \times S^2 
\]
where this identification requires the choice of a fiberwise partially hermitian metric.  
This manifold is equipped with the natural structure of a transversely holomorphic foliation (THF).
We will see that the including the backreaction corresponds to deforming this tructure. 
For sake of analogy, we think of as being a twisted version of $AdS_3 \times S^2$. \footnote{It is an interesting question if this corresponds the actual twist of a five--dimensional supersymmetric background of this form.}
We proceed to describe the twisted version of states at the boundary of this version of $AdS$.
We first proceed before turning on the backreaction.

If we choose a fiberwise partially hermitian metric on the bundle $\R \oplus K_C$ we obtain a projection $\R \times \T^*C \to \R_{>0} \times C$ which combines the fiberwise norm with the natural bundle projection.
Denote by $r$ a coordinate for the direction $\R_+$ normal to the brane and let $z \in C$ be a local holomorphic coordinate.
The fibers of this projection away from $r = 0$ are all homeomorphic to the two-sphere.

Compactification along this projection results in a theory with infinitely many Kaluza--Klein modes roughly parametrized by the Cauchy--Riemann cohomology of the two sphere as a hypersurface in $\R \oplus K_C|_z \simeq \R \times \C$.
We will elaborate on the appearance of this sort of cohomology momentarily.
The theory admits a natural `vacuum' boundary condition at $r=0$.
In local coordinates, these are fields $\alpha(t,z,w)$ on the complement to the brane which extend to regular functions along the brane.

@@

The phase space is equipped with a natural symplectic form given by
\[
\int_C \d z \oint_{S^2} \d w \, \alpha \wedge \alpha' .
\]
There is a natural Lagrangian inside of the phase space which consists of linear combinations of elements $\alpha(z) \otimes f(t,w)$ where $\alpha(z) \in \Omega^{0,\bu}(C)$ and $f(t,w)$ is a smooth function on $\R \times \C - 0$ which extends to zero.
The linearized equations of motion simply say that $\alpha$ is holomorphic, $f$ is independent of $t$ and depends holomorphically on $w$.

>>>>

The first entry of the AdS/CFT dictionary in traditional treatments is a matching between \textit{supergravity states} and local operators in the CFT \cite{}. The goal of this section is to provide constructions of spaces of supergravity states in our eleven-dimensional model, via geometric quantization. The state spaces on ${\rm AdS}_{7}\times S^{4}$ and ${\rm AdS}_{4}\times S^{7}$ have a remarkable property - they are naturally modules for certain infinite dimensional exceptional lie superalgebras. We conclude the section by computing characters for these modules and comparing them with large $N$ indices for fivebranes and membranes in the literature.

Before proceeding with the construction, let us first give some feel for the situation we hope to describe. Suppose we consider a gravitational theory on $AdS_{d+1}\times S^{d^{\prime}}$, which we compactify to view as a theory on $AdS_{d+1}$ with all Kaluza-Klein harmonics included. Let $M^{d}$ denote the conformal boundary of $AdS_{d+1}$. A supergravity state is traditionally defined to be a solution to linearized equations of motion with a given boundary value \cite{}. Typically, this definition is made in situations where the relevant boundary value problem has a unique solution, in which case one may label states by the corresponding boundary values. Moreover, one may think of such boundary values as arising from modifications of a vacuum boundary condition at a point.

\subsection{Twisted Backreactions}
We begin by describing the relevant backgrounds. In eleven-dimensional supergravity, the ${\rm AdS}_7 \times S^4$ and ${\rm AdS}_{4}\times S^{7}$ backgrounds are obtained by backreacting a number of fivebranes and membranes respectively in flat space \cite{Maldacena:1997re,WittenAdS}.
In \cite{RSW} we gave descriptions of twisted versions of these backgrounds. We will recall this construction, adapted to a slightly more global situation than is considered in \cite{RSW}.

@@

  \item Deform the theory on the complement of the zero section by a certain Maurer--Cartan element.
  The Maurer--Cartan element is thought of as the flux sourced by branes wrapping the zero section.
\end{itemize}

\parsec[s:brkevin]
As a way to highlight the key aspects of the construction, we consider the simplified model of Costello's twisted $M$ theory on $\R \times \T^* C$, where $C$ is a Riemann surface equipped with a nonvanishing holomorphic one-form $\d z$, with some number of twisted `fivebranes' wrapping the zero section
\[
0 \times C \subset \R \times \T^* C .
\]
Denote by $t$ the real coordinate and by $w$ the fiber coordinate in $\T^* C$.

If we remove the defect we obtain the manifold
\[
\left(\R \times \T^* C\right) - C \simeq C \times \R_{>0} \times S^2
\]

This manifold is equipped with the natural structure of a transversely holomorphic foliation (THF).

If we choose a fiberwise partially hermitian metric on the bundle $\R \oplus K_C$ we obtain a projection $\R \times \T^*C \to \R_{+} \times C$ which combines the fiberwise norm with the natural bundle projection.
Denote by $r$ a coordinate for the direction $\R_+$ normal to the brane and let $z \in C$ be a local holomorphic coordinate.

The fibers of this projection away from $r = 0$ are all homeomorphic to the two-sphere. Moreover, they come equipped with a canonical complexified foliation of rank 1. Compactification along this projection results in a theory with infinitely many Kaluza--Klein modes roughly parametrized by the  Cauchy--Riemann cohomology of the two sphere as a hypersurface in $\R \oplus K_C|_z \simeq \R \times \C$.

We will see that the including the backreaction corresponds to deforming this structure.
For sake of analogy, we think of the resulting deformation as being a twisted version of $AdS_3 \times S^2$. \footnote{It is an interesting question if this corresponds the actual twist of a five--dimensional supersymmetric background of this form.}
We proceed to describe the twisted version of states at the boundary of this version of $AdS$.
We first proceed before turning on the flux sourced by the brane.

The theory admits a natural `vacuum' boundary condition at $r=0$.
In local coordinates, these are fields $\alpha(t,z,w)$ on the complement to the brane which extend to regular functions along the brane.

@@

The phase space is equipped with a natural symplectic form given by
\[
\int_C \d z \oint_{S^2} \d w \, \alpha \wedge \alpha' .
\]
There is a natural Lagrangian inside of the phase space which consists of linear combinations of elements $\alpha(z) \otimes f(t,w)$ where $\alpha(z) \in \Omega^{0,\bu}(C)$ and $f(t,w)$ is a smooth function on $\R \times \C - 0$ which extends to zero.
The linearized equations of motion simply say that $\alpha$ is holomorphic, $f$ is independent of $t$ and depends holomorphically on $w$

### 2022-07-21 fivebranes/intro.tex
intro and index

\begin{slogan}[Twisted Holographic Principle]
  There is a map of factorization algebras
  \[
        (\iota^{*}\Obs_{grav})^{!}\to \Obs^{N}_{brane}
  \]

      that becomes an equivalence in the large $N$ limit.
\end{slogan}

    This statement has been tested in many examples \cite{}.

>>>>

\begin{expect}[Twisted Holographic Principle]
  There is a map of factorization algebras
  \[
        (\Obs_{grav}|_{Y})^{!}\to \Obs^{N}_{brane}
  \]

      that becomes an equivalence in the large $N$ limit.
\end{expect}

Nonetheless, the above expectation has been tested in many examples \cite{}.
